Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-12 TACAS2018/paper.tex
some comments

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Discrete dynamics using reals for systems without inputs}\label{sec:real_discrete_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \todo{these theorems need more wording. what's their goal here?}
 \begin{theorem}
 Given $\dot{\vec{x}}=\mat{A}\vec{x}$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0\\
 \mat{A}_{T}&= \mat{S}
 \left [ \begin{array}{cccc}
 e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(1)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
\vdots & & \ddots & \vdots \\
0 & \cdots & 0  &e^{T\lambda_i} \\
\end{array} \right ]
 \mat{S}^{-1}
 \label{eq:continuous_tube_dyn}\\
 &\text{where } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
 \end{align}
$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  $\vec{x}_T$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=T.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
 \end{corollary}
% \begin{proof}
% Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
% $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
%\begin{align}
% e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
%\end{align} 
%\begin{align} 
% e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{S}\mat{J}\mat{S}^{-1}\right)^k
% =\mat{S} \left (\sum_{k=0}^\infty \frac{1}{k!}\mat{J}^k\right) \mat{S}^{-1}\nonumber\\
% &=\mat{S}e^{\mat{J}}\mat{S}^{-1}
%\end{align} 
%\begin{equation}
%\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
% \end{equation}
% 
% Let $\mat{J}$ be a diagonal matrix, such that 
% $${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda_i \in \mat{J}.$$
% Let us now take a different sample rate $T_2$, such that 
% $${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda_i \in \mat{J}.$$
% We can then say that 
% \begin{equation}
% {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
% \end{equation}
% This proves the theorem for $gm(\lambda_i)=1$.
% We now note that given an exponentiated Jordan form with geometric multiplicity, the upper diagonal terms can be
% referenced to the original eigenvalues modified by the sampling rate.
%  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix.
% Then
%\begin{align}
% \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
% \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
%& \lambda_i^k  & \binom{k}{1}  \lambda_i^{k-1} & \vdots \\
%\vdots & \ddots & \ddots & \vdots \\
%& &  &\lambda_i^k \\
%\end{array} \right ] T_1^k
%\end{align}
%The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
%\begin{align}
%\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
%&=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
%&=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
%\end{align}
%which completes the proof for $gm(\lambda_i)>1$.
%\end{proof}

@@

%-------------------------------
\subsection{Transient response} 
\label{ssec:transientspecification}
%-------------------------------

@@

  \path[->] (v1) edge (q1.south);
  \path[->] (v2) edge (q2.south);
  \path[->] (vt) edge (lag.south);
  \path[->] (v1p) edge (o2.north);
  \path[->] (v2p) edge (circle.north);
  \path[->] (r) edge (gain.west);
  \path[->] (gain.east) edge (circle.west);
  \path[->] (circle.east) edge (q2.west);
  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (C.west)
   (C.east) edge (lag.west)
   (lag.east) edge (switch1.west)
   (switch2) edge (q1.west);
   (q1.east) edge (ykeast)
   (ykeast) edge (o2east);
  \path       (uksouth) edge (bdwest);
  \path[->] (bdwest) edge (Bd.west);
   (Bd.east) edge (o1.west)
   (o1.east) edge (delay.west)
   (xdsouth) edge (adeast)
   (adeast) edge (Ad.east)
   (Ad.west) edge (adwest)
   (adwest) edge (o1.south)
   (o2.west) edge (Ld.east)
   (Ld.west) edge (ldwest)
   (ldwest) edge (o1.north)
   (delay.east) edge (Cd.west)
   (Cd.north) edge (o2.south)
   (o2east) edge (o2.east)
   (xdsouth) edge (fbsouth)
   (fbsouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path[->] (Kd.north) edge (circle.south);
 \end{tikzpicture}
 \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
\end{figure*}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an Observed System}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization. We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations. For simplicity of the description, we will agregate the noises as follows:
\eta_1&=\nu_1+\nu_1'+\nu_t\\
\eta_2&=\nu_2+\nu_2'
A controllable and observable system will have the following dynamics:
\begin{align}
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
&=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k\nonumber\\
&+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
\label{eq:observer_LTI}
\end{align}
In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
reachable form and the observer error dynamics in observable form. Let 
\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}' \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\nonumber\\
\vec{y}_k
=& \mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_cf}
\end{align}
where
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
%\mat{A}_{c}=&\left[
%\begin{array}{ccccc}
%0&1&0&\cdots&0\\
%0&0&1&\cdots&0\\
%\vdots&\vdots&\vdots&\ddots&\vdots\\
%0&0&0&\cdots&1\\
%k_n-a_n&\cdots&k_i-a_i&\cdots&k_1-a_1
%\end{array}\right]
%\label{eq:cf_SISO_2}
\mat{A}_{c}=\left[
\begin{array}{cc}
\mat{0}&\mat{I}\\
k_n-a_n&\begin{array}{cc}\cdots&k_1-a_1\end{array}
\end{array}\right]&&
\mat{A}_{o}=\left[
\begin{array}{ccc}
\mat{0}&&a_n-l_n\\
&&\vdots\\
\mat{I}&&a_1-l_1
\end{array}\right]
{\setlength{\belowdisplayskip}{0pt}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}_d\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}_d\mat{T}_o^{-1}\\
\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T

>>>>

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Discrete dynamics using reals for systems without inputs}\label{sec:real_discrete_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \todo{these theorems need more wording. what's their goal here?}
 \todo{It's not clear to me why you look at all these symtems.}
 \begin{theorem}
 Given $\dot{\vec{x}}=\mat{A}\vec{x}$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0\\
 \mat{A}_{T}&= \mat{S}
 \left [ \begin{array}{cccc}
 e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(1)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
\vdots & & \ddots & \vdots \\
0 & \cdots & 0  &e^{T\lambda_i} \\
\end{array} \right ]
 \mat{S}^{-1}
 \label{eq:continuous_tube_dyn}\\
 &\text{where } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
 \end{align}
$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  $\vec{x}_T$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=T.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
 \end{corollary}
% \begin{proof}
% Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
% $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
%\begin{align}
% e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
%\end{align} 
%\begin{align} 
% e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{S}\mat{J}\mat{S}^{-1}\right)^k
% =\mat{S} \left (\sum_{k=0}^\infty \frac{1}{k!}\mat{J}^k\right) \mat{S}^{-1}\nonumber\\
% &=\mat{S}e^{\mat{J}}\mat{S}^{-1}
%\end{align} 
%\begin{equation}
%\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
% \end{equation}
% 
% Let $\mat{J}$ be a diagonal matrix, such that 
% $${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda_i \in \mat{J}.$$
% Let us now take a different sample rate $T_2$, such that 
% $${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda_i \in \mat{J}.$$
% We can then say that 
% \begin{equation}
% {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
% \end{equation}
% This proves the theorem for $gm(\lambda_i)=1$.
% We now note that given an exponentiated Jordan form with geometric multiplicity, the upper diagonal terms can be
% referenced to the original eigenvalues modified by the sampling rate.
%  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix.
% Then
%\begin{align}
% \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
% \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
%& \lambda_i^k  & \binom{k}{1}  \lambda_i^{k-1} & \vdots \\
%\vdots & \ddots & \ddots & \vdots \\
%& &  &\lambda_i^k \\
%\end{array} \right ] T_1^k
%\end{align}
%The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
%\begin{align}
%\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
%&=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
%&=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
%\end{align}
%which completes the proof for $gm(\lambda_i)>1$.
%\end{proof}

@@

%-------------------------------
\subsection{Transient response} 
\label{ssec:transientspecification}
%-------------------------------
\todo{this needs some explanation before the theorem in order to explain the purpose of this section.}

@@

  \path[->] (v1) edge (q1.south);
  \path[->] (v2) edge (q2.south);
  \path[->] (vt) edge (lag.south);
  \path[->] (v1p) edge (o2.north);
  \path[->] (v2p) edge (circle.north);
  \path[->] (r) edge (gain.west);
  \path[->] (gain.east) edge (circle.west);
  \path[->] (circle.east) edge (q2.west);
  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (C.west)
   (C.east) edge (lag.west)
   (lag.east) edge (switch1.west)
   (switch2) edge (q1.west);
  \path
   (q1.east) edge (ykeast)
   (ykeast) edge (o2east);
  \path       (uksouth) edge (bdwest);
  \path[->] (bdwest) edge (Bd.west);
  \path
   (Bd.east) edge (o1.west)
   (o1.east) edge (delay.west)
   (xdsouth) edge (adeast)
   (adeast) edge (Ad.east)
   (Ad.west) edge (adwest)
   (adwest) edge (o1.south)
   (o2.west) edge (Ld.east)
   (Ld.west) edge (ldwest)
   (ldwest) edge (o1.north)
   (delay.east) edge (Cd.west)
   (Cd.north) edge (o2.south)
   (o2east) edge (o2.east)
   (xdsouth) edge (fbsouth)
   (fbsouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path[->] (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
\end{figure*}

\todo{explain the purpose of this section, challenges etc...}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an Observed System}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization. We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations. For simplicity of the description, we will agregate the noises as follows:
\begin{align*}
\eta_1&=\nu_1+\nu_1'+\nu_t\\
\eta_2&=\nu_2+\nu_2'
\end{align*}
A controllable and observable system will have the following dynamics:
\begin{align}
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
&=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k\nonumber\\
&+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
\label{eq:observer_LTI}
\end{align}
In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
reachable form and the observer error dynamics in observable form. Let 
\begin{equation}
\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
\end{equation}
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}' \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\nonumber\\
\vec{y}_k
=& \mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_cf}
\end{align}
where
{
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
%\begin{align*}
%
%\mat{A}_{c}=&\left[
%\begin{array}{ccccc}
%0&1&0&\cdots&0\\
%0&0&1&\cdots&0\\
%\vdots&\vdots&\vdots&\ddots&\vdots\\
%0&0&0&\cdots&1\\
%k_n-a_n&\cdots&k_i-a_i&\cdots&k_1-a_1
%\end{array}\right]
%\label{eq:cf_SISO_2}
%\end{align*}
\begin{align*}
\mat{A}_{c}=\left[
\begin{array}{cc}
\mat{0}&\mat{I}\\
k_n-a_n&\begin{array}{cc}\cdots&k_1-a_1\end{array}
\end{array}\right]&&
\mat{A}_{o}=\left[
\begin{array}{ccc}
\mat{0}&&a_n-l_n\\
&&\vdots\\
\mat{I}&&a_1-l_1
\end{array}\right]
\end{align*}
}
{\setlength{\belowdisplayskip}{0pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}_d\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}_d\mat{T}_o^{-1}\\
\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}
